---
title: "Merge df"
author: "DL"
date: "24/03/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Main Processing
```{r}
library(tidyverse)
library(dplyr)
library(readxl)
library(readr)
library(stringr)
library(fuzzyjoin)
library(ggplot2)

en <- read_csv("Arch_english_inscriptions.txt")
en$english_translations <- str_match(en$`!/R Engelsk översättning`, regex("(?: [^ ]* [^ ]* )(.*)"))

# Starts from the beginning of each line
en$name <- str_match(en$`!/R Engelsk översättning`, regex("(?:^(\\S+\\s+){3})"))


master_data <- read_excel("Arch_master_spreadsheet-2.xls")

crosses_data <- read_excel("Arch_crosses_spreadsheet.xlsx")

merged <- left_join(master_data, crosses_data)

#TODO
# Attempting to merg translations
#translations <- en %>%
#  select(name, english_translations)   
#merged <- fuzzy_join(merged, en, by = c("Signum" = "name"), match_fun = str_detect)

# Renames columns
merged <-
merged %>%
 rename(
    Signature = Signum,
    Found_Location = Plats,
    Parish = Socken,
    District = Härad,
    Municipality = Kommun,
    Coordinates = Koordinater,
    Style_Grouping = Stilgruppering,
    Carver = Ristare,
    Material_Type = Materialtyp,
    Picture_Link = Bildlänk,
    Cross_Num = '#'
  )

#change

# Filters out entries with no carver data


merged <- filter(merged, 
!(merged$Carver == ('')))

# Filters out entries with no coordinate data
merged <- filter(merged, 
!(merged$Coordinates == ('')))

#Regex for matching (n): .*\(n\)

# Finds all entries in 'Carver' with '(A)'
merged$Attributed <- str_match(merged$Carver, ".*\\(A\\)")
# Finds all entries in 'Carver' with '(S)'
merged$Signed <- str_match(merged$Carver, ".*\\(S\\)")

# Summarises totals for cross types
merged$Total_A <- merged$A1 + merged$A2 + merged$A3 + merged$A4 + merged$A5 + merged$A6 + merged$A7 + merged$A8 + merged$A9
merged$Total_B <- merged$B1 + merged$B2 + merged$B3 + merged$B4
merged$Total_C <- merged$C1 + merged$C2 + merged$C3 + merged$C4 + merged$C5 + merged$C6 + merged$C7 + merged$C8 + merged$C9 + merged$C10
merged$Total_E <- merged$E1 + merged$E2 + merged$E3 + merged$E4 + merged$E5 + merged$E6 + merged$E7 + merged$E8 + merged$E9 + merged$E10
merged$Total_F <- merged$F1 + merged$F2 + merged$F3 + merged$F4
merged$Total_G <- merged$G1 + merged$G2 + merged$G3 + merged$G4 + merged$G5 + merged$G6

# read the right of the coordinates: (\d+.)$
merged$lat <- str_match(merged$Coordinates, regex("\\d+$"))

# read the left of the coordinates: ^[^.]*
merged$long <- str_match(merged$Coordinates, regex("^\\d+"))

# Filters out invalid coordinates
merged <- filter(merged, 
!(merged$lat == (' ')))


# Filters out the signed columns by runestones with multiple signatures
merged <- filter(merged, 
!(merged$Signed == (';')))



view(merged)

#TODO cut off coordinates not in lat/long form 

#merged$lat <- as.numeric(merged$lat)
#merged$long <- as.numeric(merged$long)



#strtoi(merged$lat)
#strtoi(merged$long)

ggplot(merged, aes(x = lat, y = long)) + geom_point()

```


## Notes from video masterclass 2
- Laser analysis -- see hesitant vs confident cuts between masters vs apprentices
  - Cuts (strong to fatigue)
  - ~3 days to carve
- Christian runestones (Southern Sweden Christianised before Northern) -- closer to Denmark 
  - Geographical
  - Swedish kings in the North against Christianity
- Data from 3 regions: Sweden, Denmark, Norway
- Tools = chisel + mallet
- "He died in white clothes" (Started but didnt finish Baptism)
- Runestones not by the person but by the carver -- Indivdiual commisioning compared to the person who died
- Runes %>% old norse %>% english (spirit/soul difference in English) 
  - English vs swedish vs icelandic
- Get rid of those without authors
- Filter by municpility instead of coordinates

